Deep Learning for Automatic Speech Recognition

### 2015-04-28 Paper/Paper.tex
Revisions
Still need citations across the board. Pictures? Opening hook!

\section*{Introduction}

\paragraph{} Due to the complexity of the speech stream and massive amount of variations possible, the problem of automatic speech recognition is a difficult one to address. The human speech system is comprised of a series of continually moving articulators with highly variable targets across contexts. Not only does a system need to deal with these variable contexts that cause different acoustic outputs for the same lexical target, but one also needs to properly handle physical and linguistic variation across speakers, different degrees of fluency, large vocabulary sizes, and even background noise. In this paper we examine two deep learning methods for automatic speech recognition: deep neural networks (DNNs) and convolutional neural networks (CNNs) based on the works of \cite{DBLP:journals/taslp/DahlYDA12} and  \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14} respectively.

@@

\section*{Traditional Approach} \TODO{Ryan GMM-HMMs}

\paragraph{} Before the rise of deep learning for automatic speech recognition, the primary tool utilized for acoustic modeling was the Gaussian mixture model. The driving concept behind GMMs is that the acoustic spectrum can be modeled by a mixture of multivariate Gaussians. Each Gaussian is weighted and combined to form a probability distribution for the observation. Due to the popularity of this approach, mel-frequency cepstrum coefficients (MFCCs) are the acoustic input of choice. This is because the 13 coefficients are decorrelated by the discrete cosine transform, allowing the GMM to make predictions quickly without a full covariance matrix.

\paragraph{} One thing that all three systems looked at here have in common is the use of hidden Markov models (HMMs) as an secondary structure that uses the posterior probability supplied by the acoustic model and the prior probability from a language model and tries to find the most probable word sequence for the acoustic input. Because these are fairly uniform across all models looked at, their inner workings and structure will be passed over here.

\paragraph{}

\begin{equation*}
b_{j}(o_{t}) = \sum_{m=1}^{M}c_{jm}\frac{1}{\sqrt{2\pi|\sigma_{jm}|}}\exp[(x-\mu_{jm})^T\sigma_{jm}^{-1}(o_{t}-\mu_{jm})]
\end{equation*}

where $o_{t}$ is an observation vector at time \textit{t}, $\mu_{jm}$ is a mean vector for an HMM state given the multivariate $m$, and $\sigma_{jm}$ is a covariance matrix for the same context. The likelihood function is not a true probability like what is supplied by the softmax layer in both DNNs and CNNs, but this does not matter for the HMM to work.

\paragraph{} Training of the GMMs is a much easier task than that of neural networks. The parameters can be estimated and re-estimated from training data using the iterative Expectation-Maximization (EM) algorithm. This allows us to continually recompute the mean, covariance, and mixture weight until we can accurately model the probability distributions of the training data.

\paragraph{} Deep learning has overtaken GMMs as a the primary way of building the acoustic model for ASR applications for a few reasons. One is simply due to an increase in processing power and better algorithms for training and pre-training. But arguably the main reason why deep learning performance outstrips that of GMMs is due to the overall size of the models. Artificial neural networks are able to take in multiple frames of the acoustic information as input, while GMMs typically look at a single frame and build an expert around it. ANNs normally take in from 9-11 frames, and process the center frame around that window. This extra context allows them to take into account a variety of features when modeling the posterior probabilities.

@@

\paragraph{} In this section we discuss the work on Large-Vocabulary Speech Recognition (LVSR) of \cite{DBLP:journals/taslp/DahlYDA12} consisting of a context dependent hidden markov model and deep neural network hybrid architecture (CD-HMM-DNN) for the acoustic model. We will begin with an overview of the general architecture, then explain the algorithms used for pre-training, and conclude a discussion on the general procedure for training. Discussion of experimental results for this approach are deferred to the results section so that they can be compared to the convolutional neural network approach.

@@

\paragraph{} To motivate their architecture, \cite{DBLP:journals/taslp/DahlYDA12} rely on the standard noisy channel model for speech recognition presented in \cite{jurafskyMartin} where we wish maximize the likelihood of a decoded word sequence given our input audio observations:

@@

\paragraph{} Based on this formalism, \cite{DBLP:journals/taslp/DahlYDA12} chose to use pre-trained deep neural networks to estimate $\cprob{q_t}{x_t}$ using MFCCs as DNN inputs and taking the senone posterior probabilities as DNN outputs. The transitioning between events is bested modeled by hidden markov models whose notation, $\pi, a$, and $q$ appears in Eqn. (\ref{eqn:lm:def}). Now that we have an overview of the general CD-DNN-HMM architecture, we can look at how \cite{DBLP:journals/taslp/DahlYDA12} train their model.

@@

\paragraph{} Given the DNN model we wish to fit the parameters of the model to a training set. This is usually accomplished by minimizing a likelihood function and deploying a gradient descent procedure to update the weights. One complication to this approach is that the likelihood can be computationally expensive for multilayer networks with many nodes rendering the approach unusable. As an alternative, one can attempt to optimize a computationally tractable surrogate to the likelihood. In this case the surrogate is the contrastive divergence developed by \cite{DBLP:journals/neco/Hinton02}. This sidestep enabled \cite{DBLP:journals/neco/HintonOT06} to develop an efficient pre-training process whose results can then be refined using a few iterations of the traditional result. In this portion of the paper we discuss the work of \cite{DBLP:journals/neco/Hinton02} and explain the greedy algorithm of \cite{DBLP:journals/neco/HintonOT06} before going on to discuss the high-level training procedure of \cite{DBLP:journals/taslp/DahlYDA12}.

\paragraph{} To understand the pre-training process, it is necessary to discuss Restricted Boltzmann Machines (RBM) and Deep Belief Networks (DBN). RBMs are an undirected bipartite graphical model with Gaussian distributed input nodes in a visible layer connecting to binary nodes in a hidden layer. Every possible arrangement of hidden, $h$, a visible, $v$, nodes is given a energy under the RBM model:

@@

\paragraph{} The next high-level step iteratively refines the CD-DNN-HMM. To do this, first the originally trained CD-GMM-HMM model is used to generate a raw alignment of states \TODO{figure out what it's aligning to} which is then mapped to its corresponding senone identifier. This resulting alignment is then used to refine the DBN by backpropagation. Next, the prior senone probability is estimated based on the number of frames \TODO{elaborate more on these frames somewhere} paired with the senone and the total number of frames. These estimates are then used to refine the HMM transition probabilities to maximize the features. Finally, if this newly estimated parameters do not improve accuracy against a development set, then the training procedure terminates; otherwise, the procedure repeats this high-level step.

@@

\paragraph{} In this section we explore the work done in \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14} on the performance of a convolutional neural network-hidden Markov model hybrid (CNN-HMM) for phone recognition on the TIMIT dataset and a large-vocabulary voice search task. The architecture used by \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14} is heavily inspired by the use of CNNs for image recognition tasks. In this model, temporal variability is handled by the HMM, while convolutions occur along the frequency axis of the acoustic signal. We will begin by exploring the overall structure of the network, addressing the shape of the input and looking closely at the convolution and pooling plys. We will also look at the novel concept of limited weight sharing across the network. Pre-training is similar to that used in \cite{DBLP:journals/taslp/DahlYDA12}, so we will instead focus on the fine-tuning of parameters using the back-propagation algorithm. We will then transition into the results section where we will compare the performance of the CD-DNN-HMM with that of the CNN-HMM.

@@

\paragraph{} Over the past few years, convolutional neural networks have proven to be highly successful in image recognition tasks. Not only have they achieved the highest results on the MNIST character recognition dataset\TODO{cite}, but they've even proven to outstrip hand-crafted object recognition systems on the much more complex ImageNet dataset \TODO{cite}. This success primarily originates from the networks ability to replicate lower-resolution features across the input space. They have previously been used for speech recognition in \TODO{cite} without great success. There they claim that while CNNs look promising for ASR, just taking the same structure as one built for image recognition will not suffice. For example, they used convolutions performed along the time axis. \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14} attempts to address these concerns and instead design a CNN specifically for ASR.

\paragraph{} One important aspect of the architecture used in this paper is how the input to the model is structured. Contrary to the above DNN model, the CNN model used here does not the standard MFCC features as input. Because these are decorrelated by the discrete cosine transform, they may not maintain locality, necessary for the convolutions to be meaningful. As such, they used the log-energy directly from the mel-frequency spectral coefficients (MFSC) along with their deltas and delta-deltas. Also, while the DNN model used only 11 frames as input, here they use 15 frames. These are each aligned into 1-D arrays across 40 frequency bands. This results in 45 feature maps, each with 40 features. Because there are three separate feature maps for each frame, convolutions are not applied across the time domain like previous work, but instead relegated to the HMM part of the model. Instead, convolutions occur only along the frequency axis.

\paragraph{} The network itself is constructed of 5 separate layers. After the input layer comes the convolution layer. This layer is separated into two different sub-layers called \textit{plies}. The first being the convolution ply and the second the pooling ply. Following the convolution layer are two fully-connected hidden layers with 1000 units each. The top layer of the network is a softmax output layer that provides the posterior probabilities to the HMM model. The convolution layer, despite being complex in design, actually decreases the overall model parameters by sharing weights across convolution plies. This makes it much smaller and faster to train than an equivalent DNN.

@@

\paragraph{} The primary goal of the convolution ply is to derive features from only a a local area of the input. In this paper, the input is convolved across the frequency axis with a specific filter size $F$. This means that each unit in the convolution ply draws from $F$ adjacent frequency bands. This allows for localized features to be passed up the network. These units in the convolution ply can then be arranged in their own feature maps where they share weights but originate from a large space in the lower layer. This allows for replication of features

\paragraph{} Because each feature map is only 1-D, a one-dimensional convolution operation from signal processing is applied along the frequency axis of each frame. This creates 45 new feature maps with units confined to a limited frequency range. Each of these units can be computed with the below formula:

\begin{equation*}
	Q_{j} = \sigma (\sum_{i=1}^{I}O_{i}\star w_{i,j})
\end{equation*}
where $\star$ is the convolution operator, $O_{i}$ is the \textit{i}-th input feature map, and $w_{i,j}$ is the local weight matrix.

\paragraph{} Without padding the input with dummy values, the convolution operation would produce a lower-dimensional feature map where each dimension decreases by the filter size $F-1$. If this is done, there will be the same number of units in the input feature map as in that of the convolution ply.

@@

\paragraph{}The pooling ply in the network acts as a next step from the convolution ply where the resolution of the convolution feature maps is reduced. The same number of feature maps are present, but their size is reduced by the pooling operation. This allows for the units in this ply to act as generalizations of the features in the convolution ply. Because the units from the convolution ply are localized and spatially located on the frequency axis, the pooled features will have slight invariance to small frequency shifts. The main problem with this is that once passed up to the pooling ply, a large amount of information about the spatial location of the feature is lost. Due to this, further convolution layers cannot be added above to further improve results, as this will likely lose too much resolution to be effective.

\paragraph{}The pooling function used in a CNN is normally either one of \textit{averaging} or \textit{maximization}. In this work, a max-pooling function was used throughout the network:
\begin{equation*}
p_{i,m} = \max_{n=1}^{G} q_{i, (m-1)xs+n}
\end{equation*}
where \textit{G} is the pooling size and \textit{s} is the shift size. If $G=s$, there is no overlap between pooling windows. In image processing, \TODO{cite for maxpool vs average} found that max-pooling consistently provided better results.  \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14} decided to vary these two values independently to discover whether or not this held true for acoustic processing as well.

\subsection*{Limited Weight Sharing}
\TODO{Insert picture of architecture?}

\paragraph{} In CNNs constructed for image recognition, weight sharing across neurons in the convolution ply is used to replicate features identified in a given area across the entire image. The use of weight sharing models the idea that the same feature can appear anywhere within an image. This is not the case with the speech signal, as features normally vary across frequency bands. Throwing away all shared weights would defeat the purpose of resorting to a CNN architecture though, so weights are only shared across the same frequency bands. This allows the modeling of small frequency shifts within single bands. Thus instead of sharing weights across entire convolution plies, \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14} limit their weight sharing to convolution units that act as input to the same pooling ply.

@@

\paragraph{} Due to the increased complexity of its architecture, pre-training of the CNN is also done with RBMs. But in order to account for both convolution and pooling plies, some slight modifications are needed. This results in what the authors call a convolutional RBM. The chief difference from the RBMs used in \cite{DBLP:journals/taslp/DahlYDA12} is that the activations in the convolution ply are stochastic. A multinomial distribution is placed over each pool, and so only a single unit can be active within the pooled set of units. This results in a requirement that there is no overlap between pooling units, or that limited weight sharing is used to isolate the convolution plies from one-another.

\paragraph{} Once pre-training of the CNN is completed, weights across the system are fine-tuned using the error back-propagation algorithm. This is fairly straightforward in the fully-connected higher layers, but units in the convolution plies need extra modifications due to weight sharing and sparse connections. Before describing how the algorithm is modified to handle these differences, we will review how training is done for the fully-connected units.

\paragraph{} In this architecture, for the weight matrix $W^{(l)}$ of the \textit{l}-th layer, the \textit{i}th column is represented by $w_{i}^{(l)}$. For fully-connected units we start working our way backward from the final softmax output layer \textit{L}, whose output $y_{i}$ is the estimated posterior probability of a given class:
\begin{equation*}
	y_{i} = \frac{\exp(o_{i}^{(L)})}{\sum_{j}\exp(o_{j}^{(L)})}
\end{equation*}
where $o_{i}^{(L)}$ is the activation computed as $o_{i}^{(L)} = o^{L-1}\cdot w_{i}^{(L)}$.

\paragraph{} Labels for each training example are used to perform supervised training where the cross-entropy function $Q({W^{(l)}}) = -\sum_{i}d_{i}\log{y_{i}}$ is minimized for the target \textbf{d} and softmax output \textbf{y}. By using the  stochastic gradient descent algorithm, we can calculate the necessary weight matrix updates as:
\begin{equation*}
	\triangle{W^{(l)}} = \epsilon \cdot (o^{(l-1)})' e^{(l)}
\end{equation*}
where $\epsilon$ is the learning rate and the error vector $e^{(l)}$ is computed from the final layer \textit{L}:
\begin{equation*}
	e^{(L)} = d - y
\end{equation*}
\begin{equation*}
	e^{(l)} = (e^{(l+1)}(W^{(l+1)})') \cdot o^{(l)} \cdot (1-o^{(l)}) 
\end{equation*}

\paragraph{} In order to transfer this process to the convolution plies, a sparse weight matrix $\hat{W}$ is created and the input and convolution feature maps are vectorized as $\hat{o}$ and $\hat{q}$. The sparse matrix $\hat{W}$ is used to model the filter size of the convolution ply so that the activations of the convolution ply can be easily computed as $\hat{q} = \sigma (\hat{o}\hat{W})$. This places it in the same form as the activations for the full-connected layers, and so back-propagation can be used to updates weights in the same manner as above. The main difference is that shared weights are collectively updated with the sum of their individual updates.

\paragraph{} Because the pooling plies have no weights, no learning occurs here. Despite this, errors need to be passed back to the convolution plies drawn from. Because max-pooling is used here, this is fairly straightforward. Errors are only propagated backwards to the largest unit in the group of those pooled. Units with lower activations are left alone.

>>>>

\section*{Introduction} \TODO{Intro sentence}

\paragraph{} Due to the complexity of the speech stream and massive amount of variations possible, the problem of automatic speech recognition is a difficult one to address. The human speech system is comprised of a series of continually moving articulators with highly variable targets across contexts. Systems need to deal with all of these contexts which can cause different acoustic representations for the same lexical target. One also needs to properly handle both physical and linguistic variation across speakers, differing degrees of fluency, large vocabulary sizes, and even background noise. All of these together demonstrate the need for a robust system that can account for such variance in its acoustic model.

\paragraph{} Deep learning approaches to ASR have seen recent success in addressing these issues, and appear to be the future means of constructing acoustic models. In this paper we examine two deep learning methods for automatic speech recognition: deep neural networks (DNNs) and convolutional neural networks (CNNs) based on the works of \cite{DBLP:journals/taslp/DahlYDA12} and  \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14} respectively.

@@

\section*{Traditional Approach}

\paragraph{} One thing that all three systems looked at here have in common is the use of hidden Markov models (HMMs) to form a hybrid structure with the acoustic model. This uses the posterior probability supplied by the acoustic model, the prior probability from a language model, and attempts to find the most probable word sequence for the acoustic input. Because these are fairly uniform across all models looked at, their inner workings and structure will be passed over here, but described in slightly more detail in the next section.

\paragraph{} Before the rise of deep learning for automatic speech recognition, the primary tool utilized for providing the acoustic model was the Gaussian mixture model. The driving concept behind GMMs is that the acoustic spectrum can be modeled by a mixture of multivariate Gaussians. Each Gaussian is weighted and combined to form a probability distribution for the observation. These models can then be used to derive a likelihood estimate for an HMM state. Due to the popularity of this approach, mel-frequency cepstrum coefficients (MFCCs) have become the acoustic input of choice. This is because the 13 coefficients are decorrelated by the discrete cosine transform, allowing the GMM to make predictions quickly without having to train a full covariance matrix. Below is the likelihood function used to produce something similar to a posterior probability:

\begin{equation*}
b_{j}(o_{t}) = \sum_{m=1}^{M}c_{jm}\frac{1}{\sqrt{2\pi|\sigma_{jm}|}}\exp[(x-\mu_{jm})^T\Sigma_{jm}^{-1}(o_{t}-\mu_{jm})]
\end{equation*}

where $o_{t}$ is an observation vector at time \textit{t}, $\mu_{jm}$ is a mean vector for an HMM state given the multivariate $m$, $c_{jm}$ is the corresponding weight, and $\Sigma_{jm}$ is a covariance matrix for the same context. The likelihood function is not a true probability like what is supplied by the softmax layer in both DNNs and CNNs, but the effect is the same.

\paragraph{} For classification, these likelihoods are transferred into the log domain for simple computation and fast evaluation. Training of GMMs is a much easier task than that of neural networks. The parameters can be estimated and re-estimated from training data using the iterative Expectation-Maximization (EM) algorithm. This allows us to continually recompute the mean, covariance, and mixture weight until we can accurately model the probability distributions of the training data.

\paragraph{} Despite how well GMMs work, deep learning approaches have overtaken them as the acoustic model for ASR applications for a few reasons. One is simply due to an increase in processing power and more refined algorithms for training and pre-training. But arguably the main reason why deep learning performance outstrips that of GMMs is due to the overall size of the models. For example, in \TODO{cite}, they use a CNN with around 60 million parameters and 650,000 neurons for image classification on the ImageNet dataset. For speech recognition, artificial neural networks are able to take in multiple frames of the acoustic context as input, while GMMs typically look at a single frame and build an expert around it. ANNs normally take in around 9-11 frames, and process the center frame around that window. This extra context allows them to take into account a variety of additional features when modeling the posterior probabilities.

@@

\paragraph{} In this section we discuss the work on Large-Vocabulary Speech Recognition (LVSR) of \cite{DBLP:journals/taslp/DahlYDA12} consisting of a context dependent hidden Markov model and deep neural network hybrid architecture (CD-HMM-DNN) for the acoustic model. We will begin with an overview of the general architecture, then explain the algorithms used for pre-training, and conclude with a discussion on the general procedure for training. Discussion of experimental results for this approach are deferred to the results section so that they can be compared to the convolutional neural network approach.

@@

\paragraph{} To motivate their architecture, \cite{DBLP:journals/taslp/DahlYDA12} rely on the standard noisy channel model for speech recognition presented in \cite{jurafskyMartin} where we wish to maximize the likelihood of a decoded word sequence given our input audio observations:

@@

\paragraph{} Based on this formalism, \cite{DBLP:journals/taslp/DahlYDA12} chose to use pre-trained deep neural networks to estimate $\cprob{q_t}{x_t}$ using MFCCs as DNN inputs and taking the senone posterior probabilities as DNN outputs. The transitioning between events is bested modeled by hidden Markov models whose notation, $\pi, a$, and $q$ appears in Eqn. (\ref{eqn:lm:def}). Now that we have an overview of the general CD-DNN-HMM architecture, we can look at how \cite{DBLP:journals/taslp/DahlYDA12} train their model.

@@

\paragraph{} Given the DNN model, we wish to fit the parameters of the model to a training set. This is usually accomplished by minimizing a likelihood function and deploying a gradient descent procedure to update the weights. One complication to this approach is that the likelihood can be computationally expensive for multilayer networks with many nodes rendering the approach unusable. As an alternative, one can attempt to optimize a computationally tractable surrogate to the likelihood. In this case the surrogate is the contrastive divergence developed by \cite{DBLP:journals/neco/Hinton02}. This sidestep enabled \cite{DBLP:journals/neco/HintonOT06} to develop an efficient pre-training process whose results can then be refined using a few iterations of the traditional result. In this portion of the paper we discuss the work of \cite{DBLP:journals/neco/Hinton02} and explain the greedy algorithm of \cite{DBLP:journals/neco/HintonOT06} before going on to discuss the high-level training procedure of \cite{DBLP:journals/taslp/DahlYDA12}.

\paragraph{} To understand the pre-training process, it is necessary to discuss Restricted Boltzmann Machines (RBM) and Deep Belief Networks (DBN). RBMs are an undirected bipartite graphical model with Gaussian distributed input nodes in a visible layer connecting to binary nodes in a hidden layer. Every possible arrangement of hidden, $h$, and visible, $v$, nodes is given an energy under the RBM model:

@@

\paragraph{} The next high-level step iteratively refines the CD-DNN-HMM. To do this, first the originally trained CD-GMM-HMM model is used to generate a raw alignment of states \TODO{figure out what it's aligning to} which is then mapped to its corresponding senone identifier. This resulting alignment is then used to refine the DBN by back-propagation. Next, the prior senone probability is estimated based on the number of frames \TODO{elaborate more on these frames somewhere} paired with the senone and the total number of frames. These estimates are then used to refine the HMM transition probabilities to maximize the features. Finally, if these newly estimated parameters do not improve accuracy against a development set, then the training procedure terminates; otherwise, the procedure repeats this high-level step.

@@

\paragraph{} In this section we explore the work done in \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14} with a convolutional neural network-hidden Markov model hybrid (CNN-HMM) for phone recognition on the TIMIT dataset and a large-vocabulary voice search task. The architecture used by \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14} is heavily inspired by the use of CNNs for image recognition tasks. In this model, temporal variability is handled by the HMM, while convolutions occur along the frequency axis of the acoustic signal. We will begin by exploring the overall structure of the network, addressing the shape of the input and looking closely at the convolution and pooling plys. We will also look at the novel concept of limited weight sharing across the network. Pre-training is similar to that used in \cite{DBLP:journals/taslp/DahlYDA12}, so we will instead focus on the fine-tuning of parameters using the back-propagation algorithm. We will then transition into the results section where we will compare the performance of the CD-DNN-HMM with that of the CNN-HMM.

@@

\paragraph{} Over the past few years, convolutional neural networks have proven to be highly successful in image recognition tasks. Not only have they achieved the highest results on the MNIST character recognition dataset\TODO{cite}, but they've even proven to outstrip hand-crafted object recognition systems on the much more complex ImageNet dataset \TODO{cite}. This success primarily originates from the networks ability to replicate lower-resolution features across the input space. They have also previously been used for speech recognition in \TODO{cite}, but without great success. There they claim that while CNNs look promising for ASR, just taking the same structure as one built for image recognition will not suffice. For example, in that work they used convolutions performed along the time axis. \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14} attempts to address these concerns and instead design a CNN specifically for ASR.

\paragraph{} Before discussing the network architecture itself, it's important to understand how the input to the model is structured. Contrary to the above DNN model, the CNN model used here does not use the standard MFCC features as input. Because these are decorrelated by the discrete cosine transform, they may not maintain the locality that is necessary for the convolutions to be meaningful. As such, they used the log-energy directly from the mel-frequency spectral coefficients, what they refer to as MFSC features, along with their deltas and delta-deltas. Also, while the DNN model used only 11 frames as input, here they use 15 frames as their input window. \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14} proposes two different ways of structuring these 15 frames. These could be arranged into three 2-D feature maps with frequency on one axis and time on the other. This would allow for 2-D convolutions that normalize both frequency and time domains at the same time. Instead, they opt for the second solution where each frame is aligned into 1-D arrays across the 40 frequency bands. This results in 45 feature maps, each with 40 features. Because there are three separate feature maps for each frame, convolutions are not applied across the time domain like in \TODO{cite}, but instead relegated to the HMM part of the model. Instead, convolutions occur only along the frequency axis.

\paragraph{} The network itself is constructed of 5 separate layers. After the input layer comes the convolution layer. This layer is separated into two different sub-layers called \textit{plies}. The first being the convolution ply and the second the pooling ply. These will be discussed in depth in the following sections. Following the convolution layer are two fully-connected hidden layers with 1000 units each. The top layer of the network is a softmax output layer that provides the posterior probabilities to the HMM model. The convolution layer, despite being complex in design, actually decreases the overall model parameters by sharing weights across convolution plies. This makes it much smaller and faster to train than an equivalent DNN.

@@

\paragraph{} The primary goal of the convolution ply is to derive more abstracted features from only local areas of the input. In this paper, the acoustic input is convolved across the frequency axis with a specific filter size $F$. This means that each unit in the convolution ply draws from $F$ adjacent frequency bands. This allows for localized features to be passed up the network. These units in the convolution ply can then be arranged in their own feature maps, where they share weights, but originate from a larger space in the lower layer. This allows for replication of features across certain frequency windows.

\paragraph{} Because each feature map is only 1-D, a one-dimensional convolution operation is applied along the frequency axis of each frame. This creates 45 new feature maps with units confined to a limited frequency range. Each of these units can be computed with the below formula:

\begin{equation*}
	Q_{j} = \sigma (\sum_{i=1}^{I}O_{i}\star w_{i,j})
\end{equation*}
where $\star$ is the convolution operator, $O_{i}$ is the \textit{i}-th input feature map, and $w_{i,j}$ is the local weight matrix. For each unit in the convolution ply, all input units within the filter size are multiplied by their weights, summed, and passed through a non-linear function. Without padding the input with dummy values, the convolution operation would produce a lower-dimensional feature map where each dimension decreases by the filter size $F-1$. If this addition is done, there will be the same number of units in the input feature map as in that of the convolution ply.

@@

\paragraph{}The pooling ply acts as a next step from the convolution ply, where the resolution of the convolution feature maps is reduced. While it is not necessary to follow a convolution ply with a pooling ply, in this work the two always occur together. Compared to the convolution ply, the same number of feature maps are present, but their size is reduced by the pooling operation. This allows for the units in this ply to act as generalizations of the features in the convolution ply. Because the units from the convolution ply are localized and spatially located on the frequency axis, the pooled features will have slight invariance to small frequency shifts. The main problem with this is that once passed up to the pooling ply, a large amount of information about the spatial location of the feature is lost. Due to this, further convolution layers stacked on top tend to have quickly diminishing returns in their results. This is caused by extra pooling layers likely losing too much resolution to be effective.

\paragraph{}The pooling function used in a CNN is normally either one of \textit{averaging} or \textit{maximization}. In image processing, \TODO{cite for maxpool vs average} found that max-pooling consistently provided better results over average pooling. In this work, a max-pooling function was used throughout the network:
\begin{equation*}
p_{i,m} = \max_{n=1}^{G} q_{i, (m-1)xs+n}
\end{equation*}
where \textit{G} is the pooling size and \textit{s} is the shift size. If $G=s$, there is no overlap between pooling windows. Traditionally, these are kept from overlapping to simplify the structure of the network. \TODO{cite ImageNet} found that having slight overlaps in their pooling windows actually increased performance of their system. \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14} decided to vary these two values independently to discover whether or not this held true for acoustic processing as well.

\subsection*{Limited Weight Sharing}

\paragraph{} In CNNs constructed for image recognition, weights are shared across units in the convolution ply to replicate features identified in a given area across the entire image. The use of weight sharing models the idea that the same feature can appear anywhere within an image. This is not the case with the speech signal, as observed features normally vary across frequency bands. Throwing away all shared weights would defeat the purpose of resorting to a CNN architecture though, so \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14} introduce the idea of weights only being shared across the same frequency bands. They refer to this as limited weight sharing (LWS). This allows the modeling of small frequency shifts within single bands. Thus instead of sharing weights across entire convolution plies, the experiment with limiting their weight sharing to convolution units that act as input to the same pooling ply. They experiment with both approaches, and find that LWS offers slight improvements over full weight sharing (FWS).

@@

\paragraph{} Due to the depth of its architecture, pre-training of the CNN is also done using Restricted Boltzmann Machines. But in order to account for both convolution and pooling plies, some slight modifications are needed. This results in what the authors call a convolutional RBM. The chief difference from the RBMs used in \cite{DBLP:journals/taslp/DahlYDA12} is that the activations in the convolution ply are stochastic. A multinomial distribution is placed over each pool, and so only a single unit can be active within the pooled set of units. This results in a requirement that there is no overlap between pooling units, or that limited weight sharing is used to isolate the convolution plies from one-another.

\paragraph{} Once pre-training of the CNN is completed, weights across the system are fine-tuned using the error back-propagation algorithm. This is fairly straightforward in the fully-connected higher layers, but units in the convolution plies need extra modifications due to the weight sharing and sparse connections cause by the filters. Before describing how the algorithm is modified to handle these differences, we will review how training is done for the fully-connected units.

\paragraph{} In this architecture, for the weight matrix $W^{(l)}$ of the \textit{l}-th layer, the \textit{i}th column is represented by $w_{i}^{(l)}$. For fully-connected units we start working our way backward from the final softmax output layer \textit{L}, whose output $y_{i}$ is the estimated posterior probability of a given class:
\begin{equation*}
	y_{i} = \frac{\exp(o_{i}^{(L)})}{\sum_{j}\exp(o_{j}^{(L)})}
\end{equation*}
where $o_{i}^{(L)}$ is the activation computed as $o_{i}^{(L)} = o^{L-1}\cdot w_{i}^{(L)}$ without a non-linear function.

\paragraph{} Labels for each training example are then used to perform supervised training where the goal is to minimize the cross-entropy function $Q({W^{(l)}}) = -\sum_{i}d_{i}\log{y_{i}}$ for the target \textbf{d} and softmax output \textbf{y}. By using the  stochastic gradient descent algorithm, we can calculate the necessary weight matrix updates as:
\begin{equation*}
	\triangle{W^{(l)}} = \epsilon \cdot (o^{(l-1)})' e^{(l)}
\end{equation*}
where $\epsilon$ is the learning rate and the error vector $e^{(l)}$ is computed backwards from the final layer \textit{L}:
\begin{equation*}
	e^{(L)} = d - y
\end{equation*}
\begin{equation*}
	e^{(l)} = (e^{(l+1)}(W^{(l+1)})') \cdot o^{(l)} \cdot (1-o^{(l)}) 
\end{equation*}

\paragraph{} In order to transfer this process to the convolution plies, a sparse weight matrix $\hat{W}$ is created and the input and convolution feature maps are vectorized as $\hat{o}$ and $\hat{q}$. The sparse matrix $\hat{W}$ is used to model the filter size of the convolution ply so that the activations of the convolution ply can be easily computed as $\hat{q} = \sigma (\hat{o}\hat{W})$. This places it in the same form as the activations for the fully-connected layers, and so back-propagation can be used to updates weights in the same manner as above. The main difference is that shared weights are collectively updated with the sum of their individual updates.

\paragraph{} Because the pooling plies have no weights, no learning occurs here. Despite this, errors need to be passed back to the convolution plies the draw from. Because max-pooling is used in this work, this process is fairly straightforward. Errors are only propagated backwards to the largest unit in the group of those pooled. Units with lower activations are left alone, and the weights are unaltered.
